### 2022-03-29 manuscript.tex
march29 [ci skip]
This build is based on
https://github.com/scherzerthesis/thesis/commit/c5dfe90d21403e79ce590418807f0de2cb562e01.

This commit was created by the following CI build and job:
https://github.com/scherzerthesis/thesis/commit/c5dfe90d21403e79ce590418807f0de2cb562e01/checks
https://github.com/scherzerthesis/thesis/actions/runs/2059030853

This manuscript
(\href{https://scherzerthesis.github.io/thesis/v/35b2605a594328946fa20ab6624f05dae36fa547/}{permalink})
was automatically generated
from \href{https://github.com/scherzerthesis/thesis/tree/35b2605a594328946fa20ab6624f05dae36fa547}{scherzerthesis/thesis@35b2605}
on March 29, 2022.

>>>>

This manuscript
(\href{https://scherzerthesis.github.io/thesis/v/c5dfe90d21403e79ce590418807f0de2cb562e01/}{permalink})
was automatically generated
from \href{https://github.com/scherzerthesis/thesis/tree/c5dfe90d21403e79ce590418807f0de2cb562e01}{scherzerthesis/thesis@c5dfe90}
on March 29, 2022.
